Approximating Lattice Similarity

### 2023-02-06 LatticeMatching/LM.tex
update in reply to referees 1,2,3, but not completely the "Report"

	\subsection{The space \GVI{}}
	\citeasnoun{Andrews2014} introduced the space \GVI{} based on the metric tensor
	and operated on by Niggli reductions \cite{Niggli1928}. A point in \GVI{}
	is defined by \\
	$\bf{g}$ =   [$\mathit{a^2}$, $\mathit{b^2}$, $\mathit{c^2}$, 2\vdotv{b}{c}, 2\vdotv{a}{c}, 2\vdotv{a}{b}]

@@

@@

@@

	Once the preferred result has been found, the corresponding inverted transformation is used
	to place the vector in the region of the original reduced reference cell. Finally, the inverse of the reduction
	operation that was performed on the reference cell is used to create the best match
	to the original reference. If it is desirable to restore lattice centering, then that operation must also  be
	performed.

@@

	Three example unit cells were chosen from several hundred indexed data frames.
	Two are C-centered and one is primitive. 
	Table \ref{table:signal0} is the reported data, and tables
	\ref{table:signal1}, \ref{table:signal2}, and \ref{table:signal3}
	are the approximate similarity matches.
	\begin{table}
		\begin{center}
			\caption{Adenosine receptor A2A: 5NLX.  }
~~\\

@@

	The program SAUC \cite{mcgill2014} was used to query the
	Protein Data Bank (PDB). The search started from the
	C-centered unit cell of PDB entry 1RGX (resistin) requesting the nearest 50 cells;
	26 unique cells resulted. Because there was no limit on
	how far the points could be from the probe, some cells
	differ significantly from the search cell. The results are listed
	in Table \ref{table:PDB1} in their published representation. Table \ref{tablePDB2} lists the same cells
	in the same order.

@@

	A method is proposed for transforming unit cells for a group of crystals so that they all appear
	as similar as possible to a selected cell. The search for
	cells similar to the reference cell
	 in done using the reduced cell comparing to 
	other possible unit cells nearby in the space \SVI{}. 
	At the end, the lattice centering of the reference cell
	is restored.

>>>>

%	\subsection{The space \GVI{}}
%	\citeasnoun{Andrews2014} introduced the space \GVI{} based on the metric tensor
%	and operated on by Niggli reductions \cite{Niggli1928}. A point in \GVI{}
%	is defined by \\
%	$\bf{g}$ =   [$\mathit{a^2}$, $\mathit{b^2}$, $\mathit{c^2}$, 2\vdotv{b}{c}, 2\vdotv{a}{c}, 2\vdotv{a}{b}]

@@

	Because the 24 operations defining reflection are unitary and
	in \SVI{} they are simply perturbations of the six values,
	they retain the values and signs of he six values, 
	simply rearranging the six scalars.

@@

	Although the six scalars are all negative for Selling
	reduced unit cells, the boundary transformations are
	not unitary, and so not retain the six negative values.

@@

	Once the preferred result has been found, the corresponding inverted transformation is used
	to place the vector in the region of the original reduced reference cell. Finally, the inverse of the reduction
	operation that was performed on the reference cell is used to create the best match
	to the original reference. If it is desirable to restore lattice centering, then that operation must also  be
	performed; the search returns a primitive representation
	of the unit cell.

@@

	Three example unit cells were chosen from several hundred indexed data frames.
	Two are C-centered and one is primitive. 
	Table \ref{table:signal0} is the reported data, and tables
	\ref{table:signal1}, \ref{table:signal2}, and \ref{table:signal3}
	are the approximate similarity matches.
	\begin{table}
		\begin{center}
			\caption{Adenosine receptor A2A: 5NLX, unit cells as reported.  }
~~\\

@@

	The program SAUC \cite{mcgill2014} was used to query the
	Protein Data Bank (PDB). The search started from the
	C-centered unit cell of PDB entry 1RGX (resistin) requesting the nearest 50 cells;
	26 unique cells resulted. Because there was no limit on
	how far the points could be from the probe, some cells
	differ significantly from the search cell. The results are listed
	in Table \ref{table:PDB1} in their published representation. Table \ref{tablePDB2} lists the same cells
	in the same order as in Table \ref{table:PDB1}, but with 
	the same lattice centering as 1RGX, which is the first, 
	reference entry.

@@

	A method is proposed for transforming unit cells for a group of crystals so that they all appear
	as similar as possible to a selected cell. The search for
	cells similar to the reference cell
	 in done using the reduced cell and comparing to 
	other possible unit cells nearby in the space \SVI{}. 
	At the end, the lattice centering of the reference cell
	is restored.
